---
title: "Carseats"
output: html_notebook
---


**Índice**   
1. [Chapter 3 - Exercise 10](#id1)  


<h1>Chapter 3 - Exercise 10</h1><a name='id1'></a>

This question should be answered using the Carseats data set.

```{r}
library(ISLR2)
help(Carseats)
```
```{r}
attach(Carseats)
```

<span style='color:blue'>  
A simulated data set containing sales of child car seats at 400 different stores.  
A data frame with 400 observations on the following 11 variables.  
+ ‘Sales’ Unit sales (in thousands) at each location  
+ ‘CompPrice’ Price charged by competitor at each location  
+ ‘Income’ Community income level (in thousands of dollars)  
+ ‘Advertising’ Local advertising budget for company at each location (in thousands of dollars)  
+ ‘Population’ Population size in region (in thousands)  
+ ‘Price’ Price company charges for car seats at each site  
+ ‘ShelveLoc’ A factor with levels ‘Bad’, ‘Good’ and ‘Medium’ indicating the quality of the shelving location for the car  seats at each site  
+ ‘Age’ Average age of the local population  
+ ‘Education’ Education level at each location  
+ ‘Urban’ A factor with levels ‘No’ and ‘Yes’ to indicate whether the store is in an urban or rural location  
+ ‘US’ A factor with levels ‘No’ and ‘Yes’ to indicate whether the store is in the US or not</span>

(a) Fit a multiple regression model to predict Sales using Price, Urban, and US.

```{r}
A=lm(Sales~Price+Urban+US,data=Carseats)
summary(A)
```

(b) Provide an interpretation of each coefficient in the model. Be careful, some of the variables in the model are qualitative!

<span style='color:blue'>Intercept: the sales with Urban=No and US=No, al margen del precio.  
Price: increment (negative)-0.054459 of sales for a one unit increment in price.  
UrbanYes: variation of sales (neg.) if the store is in an urban location.  
USYes: increment of sales if the store is in the US</span>


(c) Write out the model in equation form, being careful to handle the qualitative variables properly.

<span style='color:blue'>
Sales= Intercept +Price*x =>13.043469-0.054459x if the store is in rural location and out the US  
       13.043469-0.054459x-0.021916 = 13,021553-0.054459x if the store is in urban location out the US  
       13.043469-0.054459x-0.021916 +1.200573= 14,222126-0.054459x if the store is in urban location in   the US  
       13.043469-0.054459x+1.200573= 14,244042-0.054459x if the store is in urban location in the US </span>

(d) For which of the predictors can you reject the null hypothesis H_0 : β j = 0?

<span style='color:blue'>For Price and USYes because their p-values are low.</span>

(e) On the basis of your response to the previous question, fit a smaller model that only uses the predictors for which there is evidence of association with the outcome.

```{r}
B=lm(Sales~Price+US,data=Carseats)
summary(B)
```


(f) How well do the models in (a) and (e) fit the data?

<span style='color:blue'>It is practically the same RSE, R². Adjusted R² is better for the second model. It is better to have less variables. Adjusted R² penalizes excess of variables.</span>


(g) Using the model from (e), obtain 95 % confidence intervals for the coefficient(s).

```{r}
confint(B)
```


(h) Is there evidence of outliers or high leverage observations in the model from (e)?

```{r}
par(mfrow = c(2,2))
plot(B)
```


<span style='color:blue'>Outliers: No, since 51, 67, and 377 are not so far from the other points. 
Leverage: Yes, there is an observation without number. (right side)</span>
