---
title: "College"
output: html_notebook
---


**Index**
1. [Chapter 2 - Exercise 8](#id1)

<h1> Chapter 2 - Exercise 8</h1><a name='id1'></a>

This exercise relates to the College data set, which can be found in the file College.csv on the book website. It contains a number of variables for 777 different universities and colleges in the US. The variables are

+ Private : Public/private indicator  
+ Apps : Number of applications received  
+ Accept : Number of applicants accepted  
+ Enroll : Number of new students enrolled  
+ Top10perc : New students from top 10 % of high school class  
+ Top25perc : New students from top 25 % of high school class  
+ F.Undergrad : Number of full-time undergraduates  
+ P.Undergrad : Number of part-time undergraduates  
+ Outstate : Out-of-state tuition  
+ Room.Board : Room and board costs  
+ Books : Estimated book costs  
+ Personal : Estimated personal spending  
+ PhD : Percent of faculty with Ph.D.’s  
+ Terminal : Percent of faculty with terminal degree  
+ S.F.Ratio : Student/faculty ratio  
+ perc.alumni : Percent of alumni who donate  
+ Expend : Instructional expenditure per student  
+ Grad.Rate : Graduation rate  

Before reading the data into R , it can be viewed in Excel or a text editor.

(a) Use the read.csv() function to read the data into R . Call the loaded data college . Make sure that you have the directory set to the correct location for the data.

```{r}
College=read.csv('data/College.csv',header=TRUE, na.strings = '?')
```

(b) Look at the data using the View() function. You should notice that the first column is just the name of each university. We don’t really want R to treat this as data. However, it may be handy to have these names for later. Try the following commands:

```{r}
rownames( College ) <- College [ , 1]
View( College )
```

You should see that there is now a row.names column with the name of each university recorded. This means that R has given each row a name corresponding to the appropriate university. R will not try to perform calculations on the row names. However, we still need to eliminate the first column in the data where the names are stored. Try

```{r}
College <- College [ , -1]
```
```{r}
View ( College )
```

Now you should see that the first data column is Private . Note that another column labeled row.names now appears before the Private column. However, this is not a data column but rather the name that R is giving to each row.

(c) i. Use the summary() function to produce a numerical summary of the variables in the data set.

```{r}
summary(College)
```


ii. Use the pairs() function to produce a scatterplot matrix of the first ten columns or variables of the data. Recall that you can reference the first ten columns of a matrix A using A[,1:10] .

```{r}
pairs(College[,1:10])
```



iii. Use the plot() function to produce side-by-side boxplots of Outstate versus Private .

```{r}
attach(College)
plot(Outstate,Private)
```


iv. Create a new qualitative variable, called Elite , by binning the Top10perc variable. We are going to divide universities into two groups based on whether or not the proportion of students coming from the top 10% of their high school classes exceeds 50%.

```{r}
Elite <- rep( " No " , nrow ( College ) )
Elite [ Top10perc > 50] <- " Yes "
Elite <- as.factor ( Elite )
College <- data.frame ( College , Elite )
```

Use the summary() function to see how many elite universities there are. Now use the plot() function to produce side-by-side boxplots of Outstate versus Elite.

```{r}
summary(Elite)
```
```{r}
plot(Outstate, Elite)
```


v. Use the hist() function to produce some histograms with differing numbers of bins for a few of the quantitative variables. You may find the command par(mfrow = c(2, 2)) useful: it will divide the print window into four regions so that four plots can be made simultaneously. Modifying the arguments to this function will divide the screen in other ways.

```{r}
par(mfrow = c(3, 3))
hist(Accept)
hist(F.Undergrad)
hist(P.Undergrad)
hist(Books)
hist(Personal)
hist(PhD)
hist(Terminal)
hist(Expend)
hist(Grad.Rate)
```


vi. Continue exploring the data, and provide a brief summary of what you discover.

```{r}
par(mfrow = c(2, 2))
plot(Books, Terminal)
plot(Books, PhD)
plot(Personal, Terminal)
plot(Personal, Grad.Rate)
```
<span style="color:blue">
It seems that neither Books or Personal does not interfere to graduation rate and PhD, but there are some singular values with a lot of personal and/or a lot of books.
</span>

```{r}
par(mfrow = c(2, 2))
plot(Private, Terminal)
plot(Private, PhD)
plot(Private, Books)
plot(Private, Grad.Rate)
```
<span style="color:blue">Private universities have less terminal and PhD, but they have a greater graduation rate. Books are similar, but a few private universities have very large book collections.</span>