---
title: "Default"
output: html_notebook
---


**Índice**   
1. [Chapter 5 - Exercise 5](#id1)  
2. [Chapter 5 - Exercise 6](#id2)  

<h1>Chapter 5 - Exercise 5</h1><a name='id1'></a>

In Chapter 4, we used logistic regression to predict the probability of default using income and balance on the Default data set. We will now estimate the test error of this logistic regression model using the validation set approach. Do not forget to set a random seed before beginning your analysis.

```{r}
set.seed(1)
library(ISLR2)
attach(Default)
```

(a) Fit a logistic regression model that uses income and balance to predict default.

```{r}
LRM=glm(default~income+balance, data=Default, family=binomial)
summary(LRM)
```


(b) Using the validation set approach, estimate the test error of this model. In order to do this, you must perform the following steps:
i. Split the sample set into a training set and a validation set.

```{r}
d <- dim(Default)[1]
train <- sample(d,d/2)

Default.test=Default[-train,]
```


ii. Fit a multiple logistic regression model using only the training observations.

```{r}
LRM.fit <-glm(default~income+balance, data=Default, family=binomial, subset = train)
```

iii. Obtain a prediction of default status for each individual in the validation set by computing the posterior probability of default for that individual, and classifying the individual to the default category if the posterior probability is greater than 0.5.

```{r}
LRM.probs <- predict ( LRM.fit , Default.test , type = "response")
LRM.pred=rep ("No", d/2)
LRM.pred[LRM.probs>.5] = "Yes"
LRM.table=table(LRM.pred, Default.test$default)
LRM.table

```


iv. Compute the validation set error, which is the fraction of the observations in the validation set that are missclassified.

```{r}
LRM.SetError <- mean(LRM.pred != Default.test$default)
LRM.SetError
```


(c) Repeat the process in (b) three times, using three different splits of the observations into a training set and a validation set. Comment on the results obtained.

```{r}
train2 <- sample(d, d/2)

Default.test2=Default[-train2,]#cambiar Default.test2
LRM.fit2 <-glm(default~income+balance, data=Default, family=binomial, subset = train)
LRM.probs2 <- predict ( LRM.fit2 , Default.test2 , type = 'response')
LRM.pred2=rep ('No', d/2)
LRM.pred2[LRM.probs2>.5] = 'Yes'
LRM.table2=table(LRM.pred2, Default.test2$default)
LRM.SetError2 <- mean(LRM.pred2 != Default.test2$default)
LRM.SetError2
```

```{r}
train3 <- sample(d, d/2)

Default.test3=Default[-train3,]
LRM.fit3 <-glm(default~income+balance, data=Default, family=binomial, subset = train)
LRM.probs3 <- predict ( LRM.fit3 , Default.test3 , type = 'response')
LRM.pred3=rep ('No', d/2)
LRM.pred3[LRM.probs3>.5] = 'Yes'
LRM.table3=table(LRM.pred3, Default.test3$default)
LRM.SetError3 <- mean(LRM.pred3 != Default.test3$default)
LRM.SetError3
```

<span style='color:blue'>The set error increases a little.</span>


(d) Now consider a logistic regression model that predicts the probability of default using income , balance , and a dummy variable for student. Estimate the test error for this model using the validation set approach. Comment on whether or not including a dummy variable for student leads to a reduction in the test error rate.

```{r}
set.seed(1)
train4 <- sample(d, d/2)

Default.test4=Default[-train4,]
LRM.fit4 <-glm(default~income+balance+student, data=Default, family=binomial, subset = train)
LRM.probs4 <- predict ( LRM.fit4 , Default.test , type = 'response')
LRM.pred4=rep ('No', d/2)
LRM.pred4[LRM.probs4>.5] = 'Yes'
LRM.table4=table(LRM.pred4, Default.test$default)
LRM.SetError4 <- mean(LRM.pred4 != Default.test$default)
LRM.SetError4
```

<span style='color:blue'>Creating a dummy variable does not lead to a reduction of the set error rate.</span>


<h1>Chapter 5 - Exercise 6</h1><a name='id2'></a>

We continue to consider the use of a logistic regression model to predict the probability of default using income and balance on the Default data set. In particular, we will now compute estimates for the standard errors of the income and balance logistic regression coefficients in two different ways: (1) using the bootstrap, and (2) using the standard formula for computing the standard errors in the glm() function. Do not forget to set a random seed before beginning your analysis.
(a) Using the summary() and glm() functions, determine the estimated standard errors for the coefficients associated with income and balance in a multiple logistic regression model that uses both predictors.

```{r}
set.seed(1)
summary(LRM)
```


(b) Write a function, boot.fn(), that takes as input the Default data set as well as an index of the observations, and that outputs the coefficient estimates for income and balance in the multiple logistic regression model.

```{r}
boot.fn<- function (data=Default,index){
  coef(glm(default~income+balance, data=Default, family=binomial, subset = index))
}
boot.fn(Default,1:392)
```



(c) Use the boot() function together with your boot.fn() function to estimate the standard errors of the logistic regression coefficients for income and balance.

```{r}
#boot function is in the boot library
library(boot)
```


```{r}
boot(data=Default, statistic=boot.fn, R=1000)
```


(d) Comment on the estimated standard errors obtained using the glm() function and using your bootstrap function.

<span style='color:blue'>The standard errors are similar computed by both methods. The LRM estimation for the std error is accurate.</span>